---
title: "ordinal_modelling"
author: "Nicolás Sánchez-Fuenzalida"
date: "2024-02-22"
output: html_document
params:
  exp_data: 'exp1'
---

```{r read_arg, include=FALSE}
# set which experiments to analyze 
# exp1, exp2 or both
exp_data <- params$exp_data
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
# Packages
if (!require('pacman', quietly = TRUE)) install.packages('pacman'); library('pacman', quietly = TRUE)
p_load(here, readr, BayesFactor, magrittr, dplyr, purrr, stringr, ggplot2)
source(here('scripts/funcs.R'))
```

```{r}
# to reproduce results
set.seed(seed = 12345)
```

### Data

```{r}

# Read data
if (exp_data == 'both') {
  
  # Read decision data
  dec_dat <-
    bind_rows(
      read_csv(here('data/processed/decision_predicted_curve_concurrent.csv'), show_col_types = FALSE),
      read_csv(here('data/processed/decision_predicted_curve_delayed.csv'), show_col_types = FALSE)
    )
  
  # Read confidence data
  conf_dat <-
    bind_rows(
      read_csv(here('data/processed/confidence_predicted_curve_concurrent.csv'), show_col_types = FALSE),
      read_csv(here('data/processed/confidence_predicted_curve_delayed.csv'), show_col_types = FALSE)
    )
  
} else if (exp_data == 'exp1') {
  
  # Read decision data
  dec_dat <-
    bind_rows(
      read_csv(here('data/processed/decision_predicted_curve_concurrent.csv'), show_col_types = FALSE)
    )
  
  # Read confidence data
  conf_dat <-
    bind_rows(
      read_csv(here('data/processed/confidence_predicted_curve_concurrent.csv'), show_col_types = FALSE)
    )
  
} else if (exp_data == 'exp2') {
  
  # Read decision data
  dec_dat <-
    bind_rows(
      read_csv(here('data/processed/decision_predicted_curve_delayed.csv'), show_col_types = FALSE)
    )
  
  # Read confidence data
  conf_dat <-
    bind_rows(
      read_csv(here('data/processed/confidence_predicted_curve_delayed.csv'), show_col_types = FALSE)
    )
}

```

### Get PSE and PMU

```{r}

# Get PSE
dec_dat <- 
  dec_dat %>% 
  get_pse() %>% 
  ungroup() %>% 
  select(-data)

# Get PMU
conf_dat <- 
  conf_dat %>% 
  get_lowest_conf() %>% 
  ungroup() %>% 
  select(-value)

# Remove participants without point to test -------------------------------

# remove participants with bad fits
bad_fits <- read_csv(here('data/processed/bad_fits.csv'), show_col_types = FALSE)
# filter out people
dec_dat <- dec_dat %>% anti_join(bad_fits %>% select(-c(data, type)), by = join_by(confidence_type, participant, bias_source))
conf_dat <- conf_dat %>% anti_join(bad_fits %>% select(-c(data, type)), by = join_by(confidence_type, participant, bias_source))

# Calculate differences in decision PSE
dec_dat <- dec_dat %>% 
  pivot_wider(names_from = bias_direction, values_from = target_length) %>% 
  mutate(pse = short - long) %>% 
  select(-c(short, long))

# Calculate differences in confidence PMU
conf_dat <- conf_dat %>% 
  pivot_wider(names_from = bias_direction, values_from = target_length) %>% 
  mutate(pmu = short - long) %>% 
  select(-c(short, long))

```

```{r}

# Combine all data
dat <- full_join(dec_dat, conf_dat, by = join_by(confidence_type, participant, bias_source))

# Put data in long format
dat <- dat %>% 
  pivot_longer(names_to = 'task', values_to = 'value', cols = c(pse, pmu))

# Renumber participants. In both experiments participant numbers are counted from 0 so there will be overlapping in numbers.
dat <-
  dat %>%
  group_by(confidence_type, participant) %>%
  mutate(participant = sprintf('S%04d', (cur_group_id()))) %>%
  ungroup()

# Create condition code
dat <- 
  dat %>% 
  mutate(cond_code = paste0(substr(bias_source, 1, 2), substr(task, 1, 3))) 

# Sort data. This is not necessary for the analysis, it just makes the contrast plots easier to read
dat <- dat %>% 
  arrange(bias_source, task)

# Count subjects
dat %>% 
  group_by(bias_source) %>% 
  select(bias_source, participant) %>% 
  distinct() %>% 
  reframe(count = n())

# Summarize estimation
dat %>% 
  group_by(bias_source, task) %>% 
  reframe(value=mean(value)) %>% 
  pivot_wider(names_from = task, values_from = value) %>% 
  mutate(delta = pmu - pse)

```

## Get functions to create contrasts

```{r}
source(here('scripts/ordinal_model_scripts/functions_ordinal_modeling_diff_dec_conf.R'))
```

```{r}
# Contrast direction
contrast_value_pse <- -.5
contrast_value_pmu <- .5
```

## Bayes sampling

### Settings

Same settings for all models.

```{r}
# Iteration N
no_iter <- 5000
filter_iter <- .1
# R scale (effect size)
r <- .707
```

## Contrast matrices

### Subject contrast

This chunk creates a contrast matrix to indicate to which subject each observation belongs.

```{r}
# Run analysis including subject contrast?
include_id_contrast = TRUE

# Get id contrast matrix
id_contrast <- get_id_contrast(id_col = dat %>% select(participant) %>% rename(id=participant))

# Display matrix
image(t(id_contrast))

```

### Contrast A: decision & confidence are different in all conditions

```{r}
# Get contrast
X_a <- get_contrast_A(dat, val_pse = contrast_value_pse, val_pmu = contrast_value_pmu)
# Full contrast image
image(t(X_a))
# Only manipulation contrast
make_condition_contrast_image(X_a)
```

#### nWayAov

```{r}
# Get gMap
gMap <- get_gMap(X_a)
# Run nWayAOV
out <- get_bf_samp(y = dat$value, x = X_a, gMap = gMap, rscale = r, 
                   no_iter = no_iter, filter_iter = filter_iter)
# Get simple BF 
bf_out_a <- out[[1]]
# Get sampled data
samp_out_a <- out[[2]]
```

##### Check estimated values

```{r}
checkmeans_a <- with(dat, tapply(value, cond_code, mean))
pm.effest.a <- colMeans(samp_out_a)
```

Contrast A :

- mu: pay-off intercept
- beta 1: muller-lyer intercept
- beta 2: muller-lyer (pse-pmu)
- beta 3: base-rate intercept
- beta 4: base-rate (pse-pmu)
- beta 5: pay-off (pse-pmu)

```{r}

# get bias manipulation beta names
beta_names <- paste0('beta_', grep('x[0-9]{1}$', colnames(X_a)))

# Rename columns
sampled_means_a <-
  set_names(pm.effest.a[c('mu', beta_names)], c('mu', 'ml_int', 'ml_bd', 'br_int', 'br_bd', 'po_bd'))

# Compare means
checkmeans_a 
c(
  'bapmu' = sampled_means_a['mu'] + sampled_means_a['br_int'] + contrast_value_pmu * sampled_means_a['br_bd'],
  'bapse' = sampled_means_a['mu'] + sampled_means_a['br_int'] + contrast_value_pse * sampled_means_a['br_bd'],
  
  'mupmu' = sampled_means_a['mu'] + sampled_means_a['ml_int'] + contrast_value_pmu * sampled_means_a['ml_bd'],
  'mupse' = sampled_means_a['mu'] + sampled_means_a['ml_int'] + contrast_value_pse * sampled_means_a['ml_bd'],
  
  'papmu' = sampled_means_a['mu'] + contrast_value_pmu * sampled_means_a['po_bd'],
  'papse' = sampled_means_a['mu'] + contrast_value_pse * sampled_means_a['po_bd']
  
)

```

### Contrast E: decision & confidence are different in the Muller-Lyer condition, no difference in base rate and payoff

```{r}
# Get contrast
X_e <- get_contrast_E(dat, val_pse = contrast_value_pse, val_pmu = contrast_value_pmu)
# Full contrast image
image(t(X_e))
# Only manipulation contrast
make_condition_contrast_image(X_e)
```

#### nWayAov

```{r}
# Get gMap
gMap <- get_gMap(X_e)
# Run nWayAOV
out <- get_bf_samp(y = dat$value, x = X_e, gMap = gMap, rscale = r, 
                   no_iter = no_iter, filter_iter = filter_iter)
# Get simple BF 
bf_out_e <- out[[1]]
# Get sampled data
samp_out_e <- out[[2]]
```

#### Check estimated values

```{r}
pm.effest.e <- colMeans(samp_out_e)
```

Contrasts:

- mu: payoff intercept
- beta 1: muller-lyer intercept
- beta 2: muller-lyer (pse-pmu)
- beta 3: base-rate intercept

```{r}
# get bias manipulation beta names
beta_names <- paste0('beta_', grep('x[0-9]{1}$', colnames(X_e)))

# Rename columns
sampled_means_e <- 
  set_names(pm.effest.e[c('mu', beta_names)], c('mu', 'ml_int', 'ml_bd', 'br_int'))


# Sampled means
c(
  'ba' = dat %>% filter(bias_source == 'baserate') %>% reframe(value=mean(value)) %>% pull(),
  'pa' = dat %>% filter(bias_source == 'payoff') %>% reframe(value=mean(value)) %>% pull(),
  
  'mupse' = dat %>% filter(bias_source == 'mullerlyer', task == 'pse') %>% reframe(value=mean(value)) %>% pull(),
  'mupmu' = dat %>% filter(bias_source == 'mullerlyer', task == 'pmu') %>% reframe(value=mean(value)) %>% pull()
)
# Predicted means
c(
  'ba' = sampled_means_e['mu'] + sampled_means_e['br_int'],
  'pa' = sampled_means_e['mu'],
  'mupse' = sampled_means_e['mu'] + sampled_means_e['ml_int'] + contrast_value_pse * sampled_means_e['ml_bd'],
  'mupmu' = sampled_means_e['mu'] + sampled_means_e['ml_int'] + contrast_value_pmu * sampled_means_e['ml_bd']
)

```

### Contrast F: No effect in any bias source [(mulo = mush) != (balo == bash) != (palo = pash)]

```{r}
# Get contrast
X_f <- get_contrast_F(dat)
# Full contrast image
image(t(X_f))
# Only manipulation contrast
make_condition_contrast_image(X_f)
```

#### nWayAov

```{r}
# Get gMap
gMap <- get_gMap(X_f)
# Run nWayAOV
out <- get_bf_samp(y = dat$value, x = X_f, gMap = gMap, rscale = r, 
                   no_iter = no_iter, filter_iter = filter_iter)
# Get simple BF 
bf_out_f <- out[[1]]
# Get sampled data
samp_out_f <- out[[2]]
```

#### Check estimated values

Contrasts:

- mu: payoff intercept
- beta 1: muller-lyer intercept
- beta 2: base-rate intercept

```{r}
checkmeans_f <- with(dat, tapply(value, bias_source, mean))
pm.effest.f <- colMeans(samp_out_f)
```


```{r}
# get bias manipulation beta names
beta_names <- paste0('beta_', grep('x[0-9]{1}$', colnames(X_f)))

# Rename columns
sampled_means_f <- 
  set_names(pm.effest.f[c('mu', beta_names)], c('mu', 'ml_int', 'br_int'))


# Compare means
checkmeans_f
c(
  'ba' = sampled_means_f['mu'] + sampled_means_f['br_int'],
  'ml' = sampled_means_f['mu'] + sampled_means_f['ml_int'],
  'pa' = sampled_means_f['mu']
)

```

### Contrast G: Bias direction effect in base rate and Muller-Lyer, no effect in payoff [(mulo > mush) > (balo > bash) & (palo = pash)]

```{r}
# Get contrast
X_g <- get_contrast_G(dat, val_pse = contrast_value_pse, val_pmu = contrast_value_pmu)
# Full contrast image
image(t(X_g))
# Only manipulation contrast
make_condition_contrast_image(X_g)
```

#### nWayAov

```{r}
# Get gMap
gMap <- get_gMap(X_g)
# Run nWayAOV
out <- get_bf_samp(y = dat$value, x = X_g, gMap = gMap, rscale = r, 
                   no_iter = no_iter, filter_iter = filter_iter)
# Get simple BF 
bf_out_g <- out[[1]]
# Get sampled data
samp_out_g <- out[[2]]
```


#### Check estimated values

```{r}
pm.effest.g <- colMeans(samp_out_g)
```

Contrasts:

- mu: payoff intercept
- beta 1: muller-lyer intercept
- beta 2: muller-lyer (pse-pmu)
- beta 3: base-rate intercept
- beta 4: base-rate (pse-pmu)

```{r}
# get bias manipulation beta names
beta_names <- paste0('beta_', grep('x[0-9]{1}$', colnames(X_g)))

# Rename columns
sampled_means_g <- 
  set_names(pm.effest.g[c('mu', beta_names)], c('mu', 'ml_int', 'ml_bd', 'br_int', 'br_bd'))
```


```{r}

c(
  checkmeans_a[c('bapse','bapmu', 'mupse', 'mupmu')],
  'pa' = dat %>% filter(bias_source == 'payoff') %>% reframe(value=mean(value)) %>% pull()
)

c(
  'bapse' = sampled_means_g['mu'] + sampled_means_g['br_int'] - .5 * sampled_means_g['br_bd'],
  'bapmu' = sampled_means_g['mu'] + sampled_means_g['br_int'] + .5 * sampled_means_g['br_bd'],
  
  'mupse' = sampled_means_g['mu'] + sampled_means_g['ml_int'] - .5 * sampled_means_g['ml_bd'],
  'mupse' = sampled_means_g['mu'] + sampled_means_g['ml_int'] + .5 * sampled_means_g['ml_bd'],
  
  'pa' = sampled_means_g['mu']
)

```


### Contrast H: Bias direction effect in Payoff and Muller-Lyer, no effect in base rate [(mulo > mush) > (palo > pash) & (balo = bash)]

```{r}
# Get contrast
X_h <- get_contrast_H(dat, val_pse = contrast_value_pse, val_pmu = contrast_value_pmu)
# Full contrast image
image(t(X_h))
# Only manipulation contrast
make_condition_contrast_image(X_h)
```

#### nWayAov

```{r}
# Get gMap
gMap <- get_gMap(X_h)
# Run nWayAOV
out <- get_bf_samp(y = dat$value, x = X_h, gMap = gMap, rscale = r, 
                   no_iter = no_iter, filter_iter = filter_iter)
# Get simple BF 
bf_out_h <- out[[1]]
# Get sampled data
samp_out_h <- out[[2]]
```

#### Check estimated values

```{r}
pm.effest.h <- colMeans(samp_out_h)
```

Contrasts:

- mu: payoff intercept
- beta 1: muller-lyer intercept
- beta 2: muller-lyer (pse-pmu)
- beta 3: payoff intercept
- beta 4: payoff (pse-pmu)

```{r}
# get bias manipulation beta names
beta_names <- paste0('beta_', grep('x[0-9]{1}$', colnames(X_h)))

# Rename columns
sampled_means_h <- 
  set_names(pm.effest.h[c('mu', beta_names)], c('mu', 'ml_int', 'ml_bd', 'br_int', 'po_bd'))
```


```{r}

c(
  checkmeans_a[c('papse', 'papmu', 'mupse', 'mupmu')],
  'ba' = dat %>% filter(bias_source == 'baserate') %>% reframe(value=mean(value)) %>% pull()
)

c(
  
  'papse' = sampled_means_h['mu'] - .5 * sampled_means_h['po_bd'],
  'papmu' = sampled_means_h['mu'] + .5 * sampled_means_h['po_bd'],
  
  'mupse' = sampled_means_h['mu'] + sampled_means_h['ml_int'] - .5 * sampled_means_h['ml_bd'],
  'mupmu' = sampled_means_h['mu'] + sampled_means_h['ml_int'] + .5 * sampled_means_h['ml_bd'],
  
  'ba' = sampled_means_h['mu'] + sampled_means_h['br_int']
  
)

```

### Contrast I: Bias direction effect in Payoff and Base rate, no effect in payoff [(mulo > mush) > (balo > bash) & (palo = pash)]

```{r}
# Get contrast
X_i <- get_contrast_I(dat, val_pse = contrast_value_pse, val_pmu = contrast_value_pmu)
# Full contrast image
image(t(X_i))
# Only manipulation contrast
make_condition_contrast_image(X_i)
```

#### nWayAov

```{r}
# Get gMap
gMap <- get_gMap(X_i)
# Run nWayAOV
out <- get_bf_samp(y = dat$value, x = X_i, gMap = gMap, rscale = r, 
                   no_iter = no_iter, filter_iter = filter_iter)
# Get simple BF 
bf_out_i <- out[[1]]
# Get sampled data
samp_out_i <- out[[2]]
```

#### Check estimated values

```{r}
pm.effest.i <- colMeans(samp_out_i)
```

Contrasts:

- mu: payoff intercept
- beta 1: muller-lyer intercept
- beta 2: base-rate intercept
- beta 3: base-rate (pse-pmu)
- beta 4: payoff (pse-pmu)

```{r}
# get bias manipulation beta names
beta_names <- paste0('beta_', grep('x[0-9]{1}$', colnames(X_i)))

# Rename columns
sampled_means_i <- 
  set_names(pm.effest.i[c('mu', beta_names)], c('mu', 'ml_int', 'br_int', 'br_bd', 'po_bd'))
```


```{r}


c(mu = mean(checkmeans_a[c('mupse', 'mupmu')]), checkmeans_a[c('papse', 'papmu', 'bapse', 'bapmu')])

c(
  'mu' = sampled_means_i['mu'] + sampled_means_i['ml_int'],
  
  'papse' = sampled_means_i['mu'] - .5 * sampled_means_i['po_bd'],
  'papmu' = sampled_means_i['mu'] + .5 * sampled_means_i['po_bd'],
  
  'bapse' = sampled_means_i['mu'] + sampled_means_i['br_int'] - .5 * sampled_means_i['br_bd'],
  'bapmu' = sampled_means_i['mu'] + sampled_means_i['br_int'] + .5 * sampled_means_i['br_bd']
  
)

```

### Contrast J: Bias direction effect in the payoff condition, no effect in base rate and muller lyer [(palo > pash) & (balo == bash) & (mulo = mush)]

```{r}
# Get contrast
X_j <- get_contrast_J(dat, val_pse = contrast_value_pse, val_pmu = contrast_value_pmu)
# Full contrast image
image(t(X_j))
# Only manipulation contrast
make_condition_contrast_image(X_j)
```

#### nWayAov

```{r}
# Get gMap
gMap <- get_gMap(X_j)
# Run nWayAOV
out <- get_bf_samp(y = dat$value, x = X_j, gMap = gMap, rscale = r, 
                   no_iter = no_iter, filter_iter = filter_iter)
# Get simple BF 
bf_out_j <- out[[1]]
# Get sampled data
samp_out_j <- out[[2]]
```

#### Check estimated values

```{r}
pm.effest.j <- colMeans(samp_out_j)
```

Contrasts:

- mu: payoff intercept
- beta 1: muller-lyer intercept
- beta 2: base-rate intercept
- beta 3: payoff (pse-pmu)

```{r}
# get bias manipulation beta names
beta_names <- paste0('beta_', grep('x[0-9]{1}$', colnames(X_j)))

# Rename columns
sampled_means_j <- 
  set_names(pm.effest.j[c('mu', beta_names)], c('mu', 'ml_int', 'br_int', 'pa_bd'))
```


```{r}

c(
  'ba' = dat %>% filter(bias_source == 'baserate') %>% reframe(value=mean(value)) %>% pull(),
  'pa' = dat %>% filter(bias_source == 'payoff') %>% reframe(value=mean(value)) %>% pull(),
  checkmeans_a['papse'], 
  checkmeans_a['papmu']
)

c(
  
  'ba' = sampled_means_j['mu'] + sampled_means_j['br_int'],
  'mu' = sampled_means_j['mu'] + sampled_means_j['ml_int'],
  
  'papse' = sampled_means_j['mu'] - .5 * sampled_means_j['pa_bd'],
  'papmu' = sampled_means_j['mu'] + .5 * sampled_means_j['pa_bd']
  
  
)

```

### Contrast K: Bias direction effect in the base-rate condition, no effect in payoff and muller lyer [(balo > bash) & (palo == pash) & (mulo = mush)]

```{r}
# Get contrast
X_k <- get_contrast_K(dat, val_pse = contrast_value_pse, val_pmu = contrast_value_pmu)
# Full contrast image
image(t(X_k))
# Only manipulation contrast
make_condition_contrast_image(X_k)
```

#### nWayAov

```{r}
# Get gMap
gMap <- get_gMap(X_k)
# Run nWayAOV
out <- get_bf_samp(y = dat$value, x = X_k, gMap = gMap, rscale = r, 
                   no_iter = no_iter, filter_iter = filter_iter)
# Get simple BF 
bf_out_k <- out[[1]]
# Get sampled data
samp_out_k <- out[[2]]
```

#### Check estimated values

```{r}
pm.effest.k <- colMeans(samp_out_k)
```

Contrasts:

- mu: payoff intercept
- beta 1: muller-lyer intercept
- beta 2: base-rate intercept
- beta 3: payoff (pse-pmu)

```{r}
# get bias manipulation beta names
beta_names <- paste0('beta_', grep('x[0-9]{1}$', colnames(X_k)))

# Rename columns
sampled_means_k <- 
  set_names(pm.effest.k[c('mu', beta_names)], c('mu', 'ml_int', 'br_int', 'ba_bd'))

c(
  'bapse' = checkmeans_a['bapse'],
  'bapmu' = checkmeans_a['bapmu'],
  'mu' = dat %>% filter(bias_source == 'mullerlyer') %>% reframe(value=mean(value)) %>% pull(),
  'pa' = dat %>% filter(bias_source == 'payoff') %>% reframe(value=mean(value)) %>% pull()
)

c(
  
  'bapse' = sampled_means_k['mu'] + sampled_means_k['br_int'] - .5 * sampled_means_k['ba_bd'],
  'bapmu' = sampled_means_k['mu'] + sampled_means_k['br_int'] + .5 * sampled_means_k['ba_bd'],
  'mu' = sampled_means_k['mu'] + sampled_means_k['ml_int'],
  'papse' = sampled_means_k['mu'] 
  
)

```

## Priors

```{r}
# Parameters for prior sampling
R <- 1000000
mu.theta.sd <- 1
# Prior sample
ml <- rnorm(R, 0, mu.theta.sd)
br <- rnorm(R, 0, mu.theta.sd)
po <- rnorm(R, 0, mu.theta.sd)

```

## Posteriors

```{r}

# Number of participant contrast columns
add_to_beta_index <- ncol(id_contrast)

### CONTRAST A -----------------------------------------------------------------

priorA <- mean(ml > 0 & br > 0 & po > 0)

# There is an effect in all conditions
make_condition_contrast_image(X_a)

# Column names of beta columns of bias direction effects
ml_bd <- paste0('beta_', 2 + add_to_beta_index)
br_bd <- paste0('beta_', 4 + add_to_beta_index)
po_bd <- paste0('beta_', 5 + add_to_beta_index)

ml_effect <- samp_out_a[, ml_bd]
br_effect <- samp_out_a[, br_bd]
po_effect <- samp_out_a[, po_bd]

ml_pos <- ml_effect > 0
ml_neg <- ml_effect < 0
br_pos <- br_effect > 0
br_neg <- br_effect < 0
po_pos <- po_effect > 0
po_neg <- po_effect < 0

# dec > conf in all conditions
postAA <- mean(ml_pos & br_pos & po_pos)
# dec > conf in ml/br, dec < conf in po
postAB <- mean(ml_pos & br_pos & po_neg)
# dec > conf in ml/po & dec < conf in br
postAC <- mean(ml_pos & br_neg & po_pos)
# dec > conf in ml & dec < conf in br/po
postAD <- mean(ml_pos & br_neg & po_neg)
# dec > conf in br/po & dec < conf in ml
postAE <- mean(ml_neg & br_pos & po_pos)
# dec > conf in br & dec < conf in ml/po
postAF <- mean(ml_neg & br_pos & po_neg)
# dec > conf in po & dec < conf in ml/br
postAG <- mean(ml_neg & br_neg & po_pos)
#dec < conf in all condition
postAH <- mean(ml_neg & br_neg & po_neg)

### CONTRAST E -----------------------------------------------------------------

priorE <- mean(ml > 0)

# There is an effect in all conditions
make_condition_contrast_image(X_e)

# Column names of beta columns of bias direction effects
ml_bd <- paste0('beta_', 2 + add_to_beta_index)

ml_effect <- samp_out_e[, ml_bd]

ml_pos <- ml_effect > 0
ml_neg <- ml_effect < 0

# dec > conf
postEA <- mean(ml_pos)
# dec < conf 
postEB <- mean(ml_neg)

### CONTRAST F -----------------------------------------------------------------

# There is an effect in all conditions
make_condition_contrast_image(X_f)

### CONTRAST G -----------------------------------------------------------------

priorG <- mean(ml > 0 & br > 0)

# There is an effect in all conditions
make_condition_contrast_image(X_g)

# Column names of beta columns of bias direction effects
ml_bd <- paste0('beta_', 2 + add_to_beta_index)
br_bd <- paste0('beta_', 4 + add_to_beta_index)

ml_effect <- samp_out_g[, ml_bd]
br_effect <- samp_out_g[, br_bd]

ml_pos <- ml_effect > 0
ml_neg <- ml_effect < 0
br_pos <- br_effect > 0
br_neg <- br_effect < 0

# dec > conf in all conditions
postGA <- mean(ml_pos & br_pos)
# dec > conf in ml/po & dec < conf in br
postGB <- mean(ml_pos & br_neg)
# dec > conf in br/po & dec < conf in ml
postGC <- mean(ml_neg & br_pos)
# dec > conf in po & dec < conf in ml/br
postGD <- mean(ml_neg & br_neg)

### CONTRAST H -----------------------------------------------------------------

priorH <- mean(ml > 0 & po > 0)

# There is an effect in all conditions
make_condition_contrast_image(X_h)

# Column names of beta columns of bias direction effects
ml_bd <- paste0('beta_', 2 + add_to_beta_index)
po_bd <- paste0('beta_', 4 + add_to_beta_index)

ml_effect <- samp_out_h[, ml_bd]
po_effect <- samp_out_h[, po_bd]

ml_pos <- ml_effect > 0
ml_neg <- ml_effect < 0
po_pos <- po_effect > 0
po_neg <- po_effect < 0

# dec > conf in all conditions
postHA <- mean(ml_pos & po_pos)
# dec > conf in ml/po & dec < conf in br
postHB <- mean(ml_pos & po_neg)
# dec > conf in br/po & dec < conf in ml
postHC <- mean(ml_neg & po_pos)
# dec > conf in po & dec < conf in ml/br
postHD <- mean(ml_neg & po_neg)

### CONTRAST I -----------------------------------------------------------------

priorI <- mean(br > 0 & po > 0)

# There is an effect in all conditions
make_condition_contrast_image(X_i)

# Column names of beta columns of bias direction effects
br_bd <- paste0('beta_', 3 + add_to_beta_index)
po_bd <- paste0('beta_', 4 + add_to_beta_index)

br_effect <- samp_out_i[, ml_bd]
po_effect <- samp_out_i[, po_bd]

br_pos <- br_effect > 0
br_neg <- br_effect < 0
po_pos <- po_effect > 0
po_neg <- po_effect < 0

# dec > conf in all conditions
postIA <- mean(br_pos & po_pos)
# dec > conf in br/po & dec < conf in br
postIB <- mean(br_pos & po_neg)
# dec > conf in br/po & dec < conf in br
postIC <- mean(br_neg & po_pos)
# dec > conf in po & dec < conf in br/br
postID <- mean(br_neg & po_neg)


### CONTRAST J -----------------------------------------------------------------

priorJ <- mean(po > 0)

# There is an effect in all conditions
make_condition_contrast_image(X_j)

# Column names of beta columns of bias direction effects
po_bd <- paste0('beta_', 3 + add_to_beta_index)

po_effect <- samp_out_j[, po_bd]

po_pos <- po_effect > 0
po_neg <- po_effect < 0

# dec > conf
postJA <- mean(po_pos)
# dec < conf 
postJB <- mean(po_neg)

### CONTRAST K -----------------------------------------------------------------

priorK <- mean(br > 0)

# There is an effect in all conditions
make_condition_contrast_image(X_k)

# Column names of beta columns of bias direction effects
br_bd <- paste0('beta_', 3 + add_to_beta_index)

br_effect <- samp_out_k[, br_bd]

br_brs <- br_effect > 0
br_neg <- br_effect < 0

# dec > conf
postKA <- mean(br_brs)
# dec < conf 
postKB <- mean(br_neg)

```

### Calculate ordinal BF

```{r}

# Unconstrained model
bf_uN <- bf_out_f$bf

# More-constrained models ---------------------------------

# model AA
bf_AA <- log(postAA / priorA) + bf_out_a$bf
# model AB
bf_AB <- log(postAB / priorA) + bf_out_a$bf
# model AC
bf_AC <- log(postAC / priorA) + bf_out_a$bf
# model AD
bf_AD <- log(postAD / priorA) + bf_out_a$bf
# model AE
bf_AE <- log(postAE / priorA) + bf_out_a$bf
# model AF
bf_AF <- log(postAF / priorA) + bf_out_a$bf
# model AG
bf_AG <- log(postAG / priorA) + bf_out_a$bf
# model AH
bf_AH <- log(postAH / priorA) + bf_out_a$bf

# model EA
bf_EA <- log(postEA / priorE) + bf_out_e$bf
# model EB
bf_EB <- log(postEB / priorE) + bf_out_e$bf

# model GA
bf_GA <- log(postGA / priorG) + bf_out_g$bf
# model GB
bf_GB <- log(postGB / priorG) + bf_out_g$bf
# model GC
bf_GC <- log(postGC / priorG) + bf_out_g$bf
# model GD
bf_GD <- log(postGD / priorG) + bf_out_g$bf

# model HA
bf_HA <- log(postHA / priorH) + bf_out_h$bf
# model HB
bf_HB <- log(postHB / priorH) + bf_out_h$bf
# model HC
bf_HC <- log(postHC / priorH) + bf_out_h$bf
# model HD
bf_HD <- log(postHD / priorH) + bf_out_h$bf

# model IA
bf_IA <- log(postIA / priorI) + bf_out_i$bf
# model IB
bf_IB <- log(postIB / priorI) + bf_out_i$bf
# model IC
bf_IC <- log(postIC / priorI) + bf_out_i$bf
# model ID
bf_ID <- log(postID / priorI) + bf_out_i$bf

# model JA
bf_JA <- log(postJA / priorJ) + bf_out_j$bf
# model JB
bf_JB <- log(postJB / priorJ) + bf_out_j$bf

# model KA
bf_KA <- log(postKA / priorK) + bf_out_k$bf
# model KB
bf_KB <- log(postKB / priorK) + bf_out_k$bf

```

## Make table with bf values

```{r}
bfs <- 
  tribble(
    ~model, ~bf, ~model_label,
    'AA', bf_AA, 'ml+ & br+ & po+',
    'AB', bf_AB, 'ml+ & br+ & po-',
    'AC', bf_AC, 'ml+ & br- & po+',
    'AD', bf_AD, 'ml+ & br- & po-',
    'AE', bf_AE, 'ml- & br+ & po+',
    'AF', bf_AF, 'ml- & br+ & po-',
    'AG', bf_AG, 'ml- & br- & po+',
    'AH', bf_AH, 'ml- & br- & po-',
    
    'EA', bf_EA, 'ml+ & br= & po=',
    'EB', bf_EB, 'ml- & br= & po=',
    
    'GA', bf_GA, 'ml+ & br+ & po=',
    'GB', bf_GB, 'ml+ & br- & po=',
    'GC', bf_GC, 'ml- & br+ & po=',
    'GD', bf_GD, 'ml- & br- & po=',
    
    'HA', bf_HA, 'ml+ & br= & po+',
    'HB', bf_HB, 'ml+ & br= & po-',
    'HC', bf_HC, 'ml- & br= & po+',
    'HD', bf_HD, 'ml- & br= & po-',
    
    'IA', bf_IA, 'ml= & br+ & po+',
    'IB', bf_IB, 'ml= & br+ & po-',
    'IC', bf_IC, 'ml= & br- & po+',
    'ID', bf_ID, 'ml= & br- & po-',
    
    'JA', bf_JA, 'ml= & br= & po+',
    'JB', bf_JB, 'ml= & br= & po-',
    
    'KA', bf_KA, 'ml= & br+ & po=',
    'KB', bf_KB, 'ml= & br- & po=',
    
    'UN', bf_uN, 'BR & ML & PO (no effect in all manipulations)'
  )

bfs %>%
  write_csv(here(sprintf('data/ordinal_modeling/ord_models_conf-dec_%s.csv', exp_data)))

```


```{r}
bfs_based <- bfs %>% 
  mutate(baseline = bfs %>% filter(model == 'UN') %>% pull(bf),
         bf_over_baseline = bf-baseline) %>% 
  arrange(desc(bf_over_baseline)) %>% 
  filter(bf_over_baseline > 0)

bfs_based
```


```{r}
bfs_based %>% 
  mutate(bf_over_rest = exp(max(bf_over_baseline) - bf_over_baseline)) %>% filter(bf_over_rest < 100)
```